### 2020-05-16 writeup/transfer.tex
prop 3.4

\begin{proposition}\label{prop_data_size}
	In the setting of Example \ref{ex_basic}, assume that $c_1 \ge 100$ and $c_2  \ge 3$ are fixed constants.
	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
	\begin{itemize}
		\item If $d^2 < \frac{2\sigma^2}{3(c_2 - 1) p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
		\item If $d^2 > \frac{3\sigma^2}{2(c_2 - 1) p}$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $100 \le c_1 < \frac{(c_2-2)\sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{c_2 \sigma^2}{2(c_2 - 1)p d^2/3 - \sigma^2}$ and $c_1\ge 110$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$. {\cor (cannot get this because we only have some bounds. If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
\end{proposition}

>>>>

\begin{proposition}\label{prop_data_size}
	In the setting of Example \ref{ex_basic}, assume that $c_1 \ge 100$ and $c_2  \ge 3$ are fixed constants.
	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
	\begin{itemize}
		\item If $c_2 < \frac{2\sigma^2}{3p d^2} + 1$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
		\item If $c_2 > \frac{3\sigma^2}{2p d^2} + 1$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $100 \le c_1 < \frac{(c_2-2)\sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{c_2 \sigma^2}{2(c_2 - 1)p d^2/3 - \sigma^2}$ and $c_1\ge 110$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$. {\cor (cannot get this because we only have some bounds. If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
\end{proposition}
